### 2014-04-21 tex/main-body-text.tex
Just added some line endings to clean it up a bit.
added some results still working on figures

\section*{Conclusions}

>>>>

\section*{Results}

\subsection*{{\sc flock} analysis of coasta California steelhead} 
{\sc flock} was run four times using the default setting for all run parameters \textit{(initial partition = random, number of iterations = 20, number of runs = 50, LLOD threshold = 0)} for values of \textit{k} from 2 to 6. The stopping point of \textit{k}=6 was chosen because four consecutive runs with 0 length plateaus were produced. 
Run times were relatively short. The four groups of runs for the default settings averaged 217 minutes (30min SD) on an i7 3.40GHz processor with 8GB of RAM. While no plateaus were observed in any of the four groups for a \textit{k} greater than two, the plateau record varied greatly among each group for \textit{k}=2 (plateau sequences- Run1=3,2,5,6,3; Run2=2,2,2,4,3,2; Run3=2,3,2,4; and Run4=2,3,3,4,2,2,5,2). Using the plateau analysis procedure suggested by \citet{Duc&Tur2012} either \textit{k}=2 is the lower bound estimate (Run1) or there is no estimate (\textit{undecided}: Runs 2-4). Despite different conclusions, the allocation of individuals for the 'best run' from each group differed by a only a single individual. When \textit{k}=2, {\sc flock} identifies a boundary in the Russian Gulch area clustering individuals into northern and southern groups. With increased \textit{k} {\sc flock} splits individuals collected from the same stream between clusters. Increasing the number of iterations from 20 to 100 did not yield an increase in plateau length.

\section*{Conclusions}
The partition space over which {\sc flock} evaluates how individuals are clustered greatly increases with both the number of individuals and the number of clusters into which they can be partitioned. The total partition space for any given k can be defined by $\sum\limits_{i=1}^k S(n,k)$ where S(n,k) is a Stirling number of the second kind. The results of {\sc flock} depend primarily on the initial partition of individuals. It is not surprising that with 2,596 individuals we could have drastically different plateau sequences with just two clusters.
